Tropical Andes frugivore trait data Frugivoria

### 2023-07-30 code/L0/L0_TropicalAndes_frugivores_frugivoria_traits.Rmd

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

# Load required packages
```{r}

```

```{r}

```

# Summary 
```{r}
glimpse(d)
```

```{r}
print("The number of occurrences is")
nrow(d)
print("The number of species is" )
length(unique(d$species))
print("The number of families is" )
length(unique(d$family))
```

# Write data to csv
```{r}
TropicalAndes_Frugivoria_path <- file.path(output_path,"TropicalAndes_Frugivoria_frugivore_traits.csv") 
write.csv(d2, file = TropicalAndes_Frugivoria_path)
```

>>>>

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path2<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

# Retrive Frugivoria data
Using r code provided at https://portal.edirepository.org/nis/codeGeneration?packageId=edi.1220.6&statisticalFileType=r
```{r}
# Package ID: edi.1220.6 Cataloging System:https://pasta.edirepository.org.
# Data set title: Frugivoria: A trait database for birds and mammals exhibiting frugivory across contiguous Neotropical moist forests .
# Data set creator:  Beth Gerstner - Michigan State University 
# Data set creator:  Phoebe Zarnetske - Michigan State University 
# Data set creator:  Patrick Bills - Michigan State University 
# Contact:  Beth Gerstner -  Michigan State University  - gerstn11@msu.edu
# Stylesheet v2.11 for metadata conversion into program: John H. Porter, Univ. Virginia, jporter@virginia.edu 
```

## Retrive file Frugivoria: Mammal database simple
```{r}
#file 3  
inUrl3  <- "https://pasta.lternet.edu/package/data/eml/edi/1220/6/3c655f2ab1d525d1b1f05ee78153e875" 
infile3 <- tempfile()
try(download.file(inUrl3,infile3,method="curl"))
if (is.na(file.size(infile3))) download.file(inUrl3,infile3,method="auto")

 Frug_mammal <-read.csv(infile3,header=F 
          ,skip=1
            ,sep=","  
                ,quot='"' 
        , col.names=c(
                    "IUCN_species_name",     
                    "common_name",     
                    "family",     
                    "genus",     
                    "species",     
                    "subspecies",     
                    "elton_species_name",     
                    "diet_cat",     
                    "diet_source_e",     
                    "diet_breadth",     
                    "diet_level",     
                    "activity_nocturnal_e",     
                    "activity_source_e",     
                    "activity_level",     
                    "for_strat_value_e",     
                    "for_strat_certainty_e",     
                    "body_mass_e",     
                    "body_mass_level_e",     
                    "body_mass_source_e",     
                    "body_size_mm",     
                    "body_size_notes",     
                    "body_size_level",     
                    "body_size_source",     
                    "sexual_dimorphism",     
                    "sexual_dimorphism_notes",     
                    "sexual_dimorphism_level",     
                    "sexual_dimorphism_source",     
                    "longevity",     
                    "longevity_notes",     
                    "longevity_level",     
                    "longevity_source",     
                    "home_range_size",     
                    "home_range_notes",     
                    "home_range_level",     
                    "home_range_source",     
                    "habitat_specialization",     
                    "habitat_specialization_source",     
                    "generation_time",     
                    "generation_time_notes",     
                    "generation_time_level",     
                    "generation_time_source",     
                    "IUCN_category",     
                    "habitat",     
                    "habitat_breadth",     
                    "habitat_breadth_source",     
                    "habitat_level",     
                    "mean_CHELSA_bio1_1981.2010_V.2.1",     
                    "mean_CHELSA_bio12_1981.2010_V.2.1",     
                    "mean_human_fp_range_2010",     
                    "mean_human_fp_range_2020",     
                    "percent_change_hf_2010_2020",     
                    "inferred_range_sqkm",     
                    "date_data_obtained",     
                    "filled_by"    ), check.names=TRUE)

unlink(infile3)

# Fix any interval or ratio columns mistakenly read in as nominal and nominal columns read as numeric or dates read as strings

if (class(Frug_mammal$IUCN_species_name)!="factor") Frug_mammal$IUCN_species_name<- as.factor(Frug_mammal$IUCN_species_name)
if (class(Frug_mammal$common_name)!="factor") Frug_mammal$common_name<- as.factor(Frug_mammal$common_name)
if (class(Frug_mammal$family)!="factor") Frug_mammal$family<- as.factor(Frug_mammal$family)
if (class(Frug_mammal$genus)!="factor") Frug_mammal$genus<- as.factor(Frug_mammal$genus)
if (class(Frug_mammal$species)!="factor") Frug_mammal$species<- as.factor(Frug_mammal$species)
if (class(Frug_mammal$subspecies)!="factor") Frug_mammal$subspecies<- as.factor(Frug_mammal$subspecies)
if (class(Frug_mammal$elton_species_name)!="factor") Frug_mammal$elton_species_name<- as.factor(Frug_mammal$elton_species_name)
if (class(Frug_mammal$diet_cat)!="factor") Frug_mammal$diet_cat<- as.factor(Frug_mammal$diet_cat)
if (class(Frug_mammal$diet_source_e)!="factor") Frug_mammal$diet_source_e<- as.factor(Frug_mammal$diet_source_e)
if (class(Frug_mammal$diet_breadth)=="factor") Frug_mammal$diet_breadth <-as.numeric(levels(Frug_mammal$diet_breadth))[as.integer(Frug_mammal$diet_breadth) ]               
if (class(Frug_mammal$diet_breadth)=="character") Frug_mammal$diet_breadth <-as.numeric(Frug_mammal$diet_breadth)
if (class(Frug_mammal$diet_level)!="factor") Frug_mammal$diet_level<- as.factor(Frug_mammal$diet_level)
if (class(Frug_mammal$activity_nocturnal_e)!="factor") Frug_mammal$activity_nocturnal_e<- as.factor(Frug_mammal$activity_nocturnal_e)
if (class(Frug_mammal$activity_source_e)!="factor") Frug_mammal$activity_source_e<- as.factor(Frug_mammal$activity_source_e)
if (class(Frug_mammal$activity_level)!="factor") Frug_mammal$activity_level<- as.factor(Frug_mammal$activity_level)
if (class(Frug_mammal$for_strat_value_e)!="factor") Frug_mammal$for_strat_value_e<- as.factor(Frug_mammal$for_strat_value_e)
if (class(Frug_mammal$for_strat_certainty_e)!="factor") Frug_mammal$for_strat_certainty_e<- as.factor(Frug_mammal$for_strat_certainty_e)
if (class(Frug_mammal$body_mass_e)=="factor") Frug_mammal$body_mass_e <-as.numeric(levels(Frug_mammal$body_mass_e))[as.integer(Frug_mammal$body_mass_e) ]               
if (class(Frug_mammal$body_mass_e)=="character") Frug_mammal$body_mass_e <-as.numeric(Frug_mammal$body_mass_e)
if (class(Frug_mammal$body_mass_level_e)!="factor") Frug_mammal$body_mass_level_e<- as.factor(Frug_mammal$body_mass_level_e)
if (class(Frug_mammal$body_mass_source_e)!="factor") Frug_mammal$body_mass_source_e<- as.factor(Frug_mammal$body_mass_source_e)
if (class(Frug_mammal$body_size_mm)=="factor") Frug_mammal$body_size_mm <-as.numeric(levels(Frug_mammal$body_size_mm))[as.integer(Frug_mammal$body_size_mm) ]               
if (class(Frug_mammal$body_size_mm)=="character") Frug_mammal$body_size_mm <-as.numeric(Frug_mammal$body_size_mm)
if (class(Frug_mammal$body_size_notes)!="factor") Frug_mammal$body_size_notes<- as.factor(Frug_mammal$body_size_notes)
if (class(Frug_mammal$body_size_level)!="factor") Frug_mammal$body_size_level<- as.factor(Frug_mammal$body_size_level)
if (class(Frug_mammal$body_size_source)!="factor") Frug_mammal$body_size_source<- as.factor(Frug_mammal$body_size_source)
if (class(Frug_mammal$sexual_dimorphism)!="factor") Frug_mammal$sexual_dimorphism<- as.factor(Frug_mammal$sexual_dimorphism)
if (class(Frug_mammal$sexual_dimorphism_notes)!="factor") Frug_mammal$sexual_dimorphism_notes<- as.factor(Frug_mammal$sexual_dimorphism_notes)
if (class(Frug_mammal$sexual_dimorphism_level)!="factor") Frug_mammal$sexual_dimorphism_level<- as.factor(Frug_mammal$sexual_dimorphism_level)
if (class(Frug_mammal$sexual_dimorphism_source)!="factor") Frug_mammal$sexual_dimorphism_source<- as.factor(Frug_mammal$sexual_dimorphism_source)
if (class(Frug_mammal$longevity)=="factor") Frug_mammal$longevity <-as.numeric(levels(Frug_mammal$longevity))[as.integer(Frug_mammal$longevity) ]               
if (class(Frug_mammal$longevity)=="character") Frug_mammal$longevity <-as.numeric(Frug_mammal$longevity)
if (class(Frug_mammal$longevity_notes)!="factor") Frug_mammal$longevity_notes<- as.factor(Frug_mammal$longevity_notes)
if (class(Frug_mammal$longevity_level)!="factor") Frug_mammal$longevity_level<- as.factor(Frug_mammal$longevity_level)
if (class(Frug_mammal$longevity_source)!="factor") Frug_mammal$longevity_source<- as.factor(Frug_mammal$longevity_source)
if (class(Frug_mammal$home_range_size)=="factor") Frug_mammal$home_range_size <-as.numeric(levels(Frug_mammal$home_range_size))[as.integer(Frug_mammal$home_range_size) ]               
if (class(Frug_mammal$home_range_size)=="character") Frug_mammal$home_range_size <-as.numeric(Frug_mammal$home_range_size)
if (class(Frug_mammal$home_range_notes)!="factor") Frug_mammal$home_range_notes<- as.factor(Frug_mammal$home_range_notes)
if (class(Frug_mammal$home_range_level)!="factor") Frug_mammal$home_range_level<- as.factor(Frug_mammal$home_range_level)
if (class(Frug_mammal$home_range_source)!="factor") Frug_mammal$home_range_source<- as.factor(Frug_mammal$home_range_source)
if (class(Frug_mammal$habitat_specialization)!="factor") Frug_mammal$habitat_specialization<- as.factor(Frug_mammal$habitat_specialization)
if (class(Frug_mammal$habitat_specialization_source)!="factor") Frug_mammal$habitat_specialization_source<- as.factor(Frug_mammal$habitat_specialization_source)
if (class(Frug_mammal$generation_time)=="factor") Frug_mammal$generation_time <-as.numeric(levels(Frug_mammal$generation_time))[as.integer(Frug_mammal$generation_time) ]               
if (class(Frug_mammal$generation_time)=="character") Frug_mammal$generation_time <-as.numeric(Frug_mammal$generation_time)
if (class(Frug_mammal$generation_time_notes)!="factor") Frug_mammal$generation_time_notes<- as.factor(Frug_mammal$generation_time_notes)
if (class(Frug_mammal$generation_time_level)!="factor") Frug_mammal$generation_time_level<- as.factor(Frug_mammal$generation_time_level)
if (class(Frug_mammal$generation_time_source)!="factor") Frug_mammal$generation_time_source<- as.factor(Frug_mammal$generation_time_source)
if (class(Frug_mammal$IUCN_category)!="factor") Frug_mammal$IUCN_category<- as.factor(Frug_mammal$IUCN_category)
if (class(Frug_mammal$habitat)!="factor") Frug_mammal$habitat<- as.factor(Frug_mammal$habitat)
if (class(Frug_mammal$habitat_breadth)=="factor") Frug_mammal$habitat_breadth <-as.numeric(levels(Frug_mammal$habitat_breadth))[as.integer(Frug_mammal$habitat_breadth) ]               
if (class(Frug_mammal$habitat_breadth)=="character") Frug_mammal$habitat_breadth <-as.numeric(Frug_mammal$habitat_breadth)
if (class(Frug_mammal$habitat_breadth_source)!="factor") Frug_mammal$habitat_breadth_source<- as.factor(Frug_mammal$habitat_breadth_source)
if (class(Frug_mammal$habitat_level)!="factor") Frug_mammal$habitat_level<- as.factor(Frug_mammal$habitat_level)
if (class(Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1)=="factor") Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1 <-as.numeric(levels(Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1))[as.integer(Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1) ]               
if (class(Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1)=="character") Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1 <-as.numeric(Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1)
if (class(Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1)=="factor") Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1 <-as.numeric(levels(Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1))[as.integer(Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1) ]               
if (class(Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1)=="character") Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1 <-as.numeric(Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1)
if (class(Frug_mammal$mean_human_fp_range_2010)=="factor") Frug_mammal$mean_human_fp_range_2010 <-as.numeric(levels(Frug_mammal$mean_human_fp_range_2010))[as.integer(Frug_mammal$mean_human_fp_range_2010) ]               
if (class(Frug_mammal$mean_human_fp_range_2010)=="character") Frug_mammal$mean_human_fp_range_2010 <-as.numeric(Frug_mammal$mean_human_fp_range_2010)
if (class(Frug_mammal$mean_human_fp_range_2020)=="factor") Frug_mammal$mean_human_fp_range_2020 <-as.numeric(levels(Frug_mammal$mean_human_fp_range_2020))[as.integer(Frug_mammal$mean_human_fp_range_2020) ]               
if (class(Frug_mammal$mean_human_fp_range_2020)=="character") Frug_mammal$mean_human_fp_range_2020 <-as.numeric(Frug_mammal$mean_human_fp_range_2020)
if (class(Frug_mammal$percent_change_hf_2010_2020)=="factor") Frug_mammal$percent_change_hf_2010_2020 <-as.numeric(levels(Frug_mammal$percent_change_hf_2010_2020))[as.integer(Frug_mammal$percent_change_hf_2010_2020) ]               
if (class(Frug_mammal$percent_change_hf_2010_2020)=="character") Frug_mammal$percent_change_hf_2010_2020 <-as.numeric(Frug_mammal$percent_change_hf_2010_2020)
if (class(Frug_mammal$inferred_range_sqkm)=="factor") Frug_mammal$inferred_range_sqkm <-as.numeric(levels(Frug_mammal$inferred_range_sqkm))[as.integer(Frug_mammal$inferred_range_sqkm) ]               
if (class(Frug_mammal$inferred_range_sqkm)=="character") Frug_mammal$inferred_range_sqkm <-as.numeric(Frug_mammal$inferred_range_sqkm)
if (class(Frug_mammal$date_data_obtained)!="factor") Frug_mammal$date_data_obtained<- as.factor(Frug_mammal$date_data_obtained)
if (class(Frug_mammal$filled_by)!="factor") Frug_mammal$filled_by<- as.factor(Frug_mammal$filled_by)

# Convert Missing Values to NA for non-dates

Frug_mammal$common_name <- as.factor(ifelse((trimws(as.character(Frug_mammal$common_name))==trimws("NA")),NA,as.character(Frug_mammal$common_name)))
Frug_mammal$subspecies <- as.factor(ifelse((trimws(as.character(Frug_mammal$subspecies))==trimws("NA")),NA,as.character(Frug_mammal$subspecies)))
Frug_mammal$diet_level <- as.factor(ifelse((trimws(as.character(Frug_mammal$diet_level))==trimws("NA")),NA,as.character(Frug_mammal$diet_level)))
Frug_mammal$activity_level <- as.factor(ifelse((trimws(as.character(Frug_mammal$activity_level))==trimws("NA")),NA,as.character(Frug_mammal$activity_level)))
Frug_mammal$body_size_mm <- ifelse((trimws(as.character(Frug_mammal$body_size_mm))==trimws("NA")),NA,Frug_mammal$body_size_mm)               
suppressWarnings(Frug_mammal$body_size_mm <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$body_size_mm))==as.character(as.numeric("NA"))),NA,Frug_mammal$body_size_mm))
Frug_mammal$body_size_notes <- as.factor(ifelse((trimws(as.character(Frug_mammal$body_size_notes))==trimws("NA")),NA,as.character(Frug_mammal$body_size_notes)))
Frug_mammal$body_size_level <- as.factor(ifelse((trimws(as.character(Frug_mammal$body_size_level))==trimws("NA")),NA,as.character(Frug_mammal$body_size_level)))
Frug_mammal$body_size_source <- as.factor(ifelse((trimws(as.character(Frug_mammal$body_size_source))==trimws("NA")),NA,as.character(Frug_mammal$body_size_source)))
Frug_mammal$sexual_dimorphism <- as.factor(ifelse((trimws(as.character(Frug_mammal$sexual_dimorphism))==trimws("NA")),NA,as.character(Frug_mammal$sexual_dimorphism)))
Frug_mammal$sexual_dimorphism <- as.factor(ifelse((trimws(as.character(Frug_mammal$sexual_dimorphism))==trimws("NA ")),NA,as.character(Frug_mammal$sexual_dimorphism)))
Frug_mammal$sexual_dimorphism_notes <- as.factor(ifelse((trimws(as.character(Frug_mammal$sexual_dimorphism_notes))==trimws("NA")),NA,as.character(Frug_mammal$sexual_dimorphism_notes)))
Frug_mammal$sexual_dimorphism_level <- as.factor(ifelse((trimws(as.character(Frug_mammal$sexual_dimorphism_level))==trimws("NA")),NA,as.character(Frug_mammal$sexual_dimorphism_level)))
Frug_mammal$sexual_dimorphism_source <- as.factor(ifelse((trimws(as.character(Frug_mammal$sexual_dimorphism_source))==trimws("NA")),NA,as.character(Frug_mammal$sexual_dimorphism_source)))
Frug_mammal$longevity <- ifelse((trimws(as.character(Frug_mammal$longevity))==trimws("NA")),NA,Frug_mammal$longevity)               
suppressWarnings(Frug_mammal$longevity <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$longevity))==as.character(as.numeric("NA"))),NA,Frug_mammal$longevity))
Frug_mammal$longevity_notes <- as.factor(ifelse((trimws(as.character(Frug_mammal$longevity_notes))==trimws("NA")),NA,as.character(Frug_mammal$longevity_notes)))
Frug_mammal$longevity_level <- as.factor(ifelse((trimws(as.character(Frug_mammal$longevity_level))==trimws("NA")),NA,as.character(Frug_mammal$longevity_level)))
Frug_mammal$longevity_source <- as.factor(ifelse((trimws(as.character(Frug_mammal$longevity_source))==trimws("NA")),NA,as.character(Frug_mammal$longevity_source)))
Frug_mammal$home_range_size <- ifelse((trimws(as.character(Frug_mammal$home_range_size))==trimws("NA")),NA,Frug_mammal$home_range_size)               
suppressWarnings(Frug_mammal$home_range_size <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$home_range_size))==as.character(as.numeric("NA"))),NA,Frug_mammal$home_range_size))
Frug_mammal$home_range_notes <- as.factor(ifelse((trimws(as.character(Frug_mammal$home_range_notes))==trimws("NA")),NA,as.character(Frug_mammal$home_range_notes)))
Frug_mammal$home_range_level <- as.factor(ifelse((trimws(as.character(Frug_mammal$home_range_level))==trimws("NA")),NA,as.character(Frug_mammal$home_range_level)))
Frug_mammal$home_range_source <- as.factor(ifelse((trimws(as.character(Frug_mammal$home_range_source))==trimws("NA")),NA,as.character(Frug_mammal$home_range_source)))
Frug_mammal$habitat_specialization <- as.factor(ifelse((trimws(as.character(Frug_mammal$habitat_specialization))==trimws("NA")),NA,as.character(Frug_mammal$habitat_specialization)))
Frug_mammal$habitat_specialization_source <- as.factor(ifelse((trimws(as.character(Frug_mammal$habitat_specialization_source))==trimws("NA")),NA,as.character(Frug_mammal$habitat_specialization_source)))
Frug_mammal$generation_time <- ifelse((trimws(as.character(Frug_mammal$generation_time))==trimws("NA")),NA,Frug_mammal$generation_time)               
suppressWarnings(Frug_mammal$generation_time <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$generation_time))==as.character(as.numeric("NA"))),NA,Frug_mammal$generation_time))
Frug_mammal$generation_time_notes <- as.factor(ifelse((trimws(as.character(Frug_mammal$generation_time_notes))==trimws("NA")),NA,as.character(Frug_mammal$generation_time_notes)))
Frug_mammal$generation_time_level <- as.factor(ifelse((trimws(as.character(Frug_mammal$generation_time_level))==trimws("NA")),NA,as.character(Frug_mammal$generation_time_level)))
Frug_mammal$generation_time_source <- as.factor(ifelse((trimws(as.character(Frug_mammal$generation_time_source))==trimws("NA")),NA,as.character(Frug_mammal$generation_time_source)))
Frug_mammal$habitat_breadth <- ifelse((trimws(as.character(Frug_mammal$habitat_breadth))==trimws("NA")),NA,Frug_mammal$habitat_breadth)               
suppressWarnings(Frug_mammal$habitat_breadth <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$habitat_breadth))==as.character(as.numeric("NA"))),NA,Frug_mammal$habitat_breadth))
Frug_mammal$habitat_level <- as.factor(ifelse((trimws(as.character(Frug_mammal$habitat_level))==trimws("NA")),NA,as.character(Frug_mammal$habitat_level)))
Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1 <- ifelse((trimws(as.character(Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1))==trimws("NA")),NA,Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1)               
suppressWarnings(Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1 <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1))==as.character(as.numeric("NA"))),NA,Frug_mammal$mean_CHELSA_bio1_1981.2010_V.2.1))
Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1 <- ifelse((trimws(as.character(Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1))==trimws("NA")),NA,Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1)               
suppressWarnings(Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1 <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1))==as.character(as.numeric("NA"))),NA,Frug_mammal$mean_CHELSA_bio12_1981.2010_V.2.1))
Frug_mammal$mean_human_fp_range_2010 <- ifelse((trimws(as.character(Frug_mammal$mean_human_fp_range_2010))==trimws("NA")),NA,Frug_mammal$mean_human_fp_range_2010)               
suppressWarnings(Frug_mammal$mean_human_fp_range_2010 <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$mean_human_fp_range_2010))==as.character(as.numeric("NA"))),NA,Frug_mammal$mean_human_fp_range_2010))
Frug_mammal$mean_human_fp_range_2020 <- ifelse((trimws(as.character(Frug_mammal$mean_human_fp_range_2020))==trimws("NA")),NA,Frug_mammal$mean_human_fp_range_2020)               
suppressWarnings(Frug_mammal$mean_human_fp_range_2020 <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$mean_human_fp_range_2020))==as.character(as.numeric("NA"))),NA,Frug_mammal$mean_human_fp_range_2020))
Frug_mammal$percent_change_hf_2010_2020 <- ifelse((trimws(as.character(Frug_mammal$percent_change_hf_2010_2020))==trimws("NA")),NA,Frug_mammal$percent_change_hf_2010_2020)               
suppressWarnings(Frug_mammal$percent_change_hf_2010_2020 <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$percent_change_hf_2010_2020))==as.character(as.numeric("NA"))),NA,Frug_mammal$percent_change_hf_2010_2020))
Frug_mammal$inferred_range_sqkm <- ifelse((trimws(as.character(Frug_mammal$inferred_range_sqkm))==trimws("NA")),NA,Frug_mammal$inferred_range_sqkm)               
suppressWarnings(Frug_mammal$inferred_range_sqkm <- ifelse(!is.na(as.numeric("NA")) & (trimws(as.character(Frug_mammal$inferred_range_sqkm))==as.character(as.numeric("NA"))),NA,Frug_mammal$inferred_range_sqkm))
Frug_mammal$date_data_obtained <- as.factor(ifelse((trimws(as.character(Frug_mammal$date_data_obtained))==trimws("NA")),NA,as.character(Frug_mammal$date_data_obtained)))

# Here is the structure of the input data frame:
str(Frug_mammal)                            
attach(Frug_mammal)                            
# The analyses below are basic descriptions of the variables. After testing, they should be replaced.

summary(IUCN_species_name)
summary(common_name)
summary(family)
summary(genus)
summary(species)
summary(subspecies)
summary(elton_species_name)
summary(diet_cat)
summary(diet_source_e)
summary(diet_breadth)
summary(diet_level)
summary(activity_nocturnal_e)
summary(activity_source_e)
summary(activity_level)
summary(for_strat_value_e)
summary(for_strat_certainty_e)
summary(body_mass_e)
summary(body_mass_level_e)
summary(body_mass_source_e)
summary(body_size_mm)
summary(body_size_notes)
summary(body_size_level)
summary(body_size_source)
summary(sexual_dimorphism)
summary(sexual_dimorphism_notes)
summary(sexual_dimorphism_level)
summary(sexual_dimorphism_source)
summary(longevity)
summary(longevity_notes)
summary(longevity_level)
summary(longevity_source)
summary(home_range_size)
summary(home_range_notes)
summary(home_range_level)
summary(home_range_source)
summary(habitat_specialization)
summary(habitat_specialization_source)
summary(generation_time)
summary(generation_time_notes)
summary(generation_time_level)
summary(generation_time_source)
summary(IUCN_category)
summary(habitat)
summary(habitat_breadth)
summary(habitat_breadth_source)
summary(habitat_level)
summary(mean_CHELSA_bio1_1981.2010_V.2.1)
summary(mean_CHELSA_bio12_1981.2010_V.2.1)
summary(mean_human_fp_range_2010)
summary(mean_human_fp_range_2020)
summary(percent_change_hf_2010_2020)
summary(inferred_range_sqkm)
summary(date_data_obtained)
summary(filled_by) 
                # Get more details on character variables

summary(as.factor(Frug_mammal$IUCN_species_name)) 
summary(as.factor(Frug_mammal$common_name)) 
summary(as.factor(Frug_mammal$family)) 
summary(as.factor(Frug_mammal$genus)) 
summary(as.factor(Frug_mammal$species)) 
summary(as.factor(Frug_mammal$subspecies)) 
summary(as.factor(Frug_mammal$elton_species_name)) 
summary(as.factor(Frug_mammal$diet_cat)) 
summary(as.factor(Frug_mammal$diet_source_e)) 
summary(as.factor(Frug_mammal$diet_level)) 
summary(as.factor(Frug_mammal$activity_nocturnal_e)) 
summary(as.factor(Frug_mammal$activity_source_e)) 
summary(as.factor(Frug_mammal$activity_level)) 
summary(as.factor(Frug_mammal$for_strat_value_e)) 
summary(as.factor(Frug_mammal$for_strat_certainty_e)) 
summary(as.factor(Frug_mammal$body_mass_level_e)) 
summary(as.factor(Frug_mammal$body_mass_source_e)) 
summary(as.factor(Frug_mammal$body_size_notes)) 
summary(as.factor(Frug_mammal$body_size_level)) 
summary(as.factor(Frug_mammal$body_size_source)) 
summary(as.factor(Frug_mammal$sexual_dimorphism)) 
summary(as.factor(Frug_mammal$sexual_dimorphism_notes)) 
summary(as.factor(Frug_mammal$sexual_dimorphism_level)) 
summary(as.factor(Frug_mammal$sexual_dimorphism_source)) 
summary(as.factor(Frug_mammal$longevity_notes)) 
summary(as.factor(Frug_mammal$longevity_level)) 
summary(as.factor(Frug_mammal$longevity_source)) 
summary(as.factor(Frug_mammal$home_range_notes)) 
summary(as.factor(Frug_mammal$home_range_level)) 
summary(as.factor(Frug_mammal$home_range_source)) 
summary(as.factor(Frug_mammal$habitat_specialization)) 
summary(as.factor(Frug_mammal$habitat_specialization_source)) 
summary(as.factor(Frug_mammal$generation_time_notes)) 
summary(as.factor(Frug_mammal$generation_time_level)) 
summary(as.factor(Frug_mammal$generation_time_source)) 
summary(as.factor(Frug_mammal$IUCN_category)) 
summary(as.factor(Frug_mammal$habitat)) 
summary(as.factor(Frug_mammal$habitat_breadth_source)) 
summary(as.factor(Frug_mammal$habitat_level)) 
summary(as.factor(Frug_mammal$date_data_obtained)) 
summary(as.factor(Frug_mammal$filled_by))
detach(Frug_mammal) 
```

## Retrive file Frugivoria: Bird database simple
```{r}
#file 4
inUrl4  <- "https://pasta.lternet.edu/package/data/eml/edi/1220/6/5a86fde71322a1ff64d94ace0ed1982c" 
infile4 <- tempfile()
try(download.file(inUrl4,infile4,method="curl"))
if (is.na(file.size(infile4))) download.file(inUrl4,infile4,method="auto")

 Frug_bird <-read.csv(infile4,header=F 
          ,skip=1
            ,sep=","  
                ,quot='"' 
        , col.names=c(
                    "IUCN_species_name",     
                    "common_name",     
                    "family_e",     
                    "genus",     
                    "species",     
                    "elton_species_name",     
                    "diet_cat_e",     
                    "diet_source_e",     
                    "diet_breadth",     
                    "diet_level",     
                    "activity_nocturnal_e",     
                    "for_strat_ground_e",     
                    "for_strat_understory_e",     
                    "for_strat_midhigh_e",     
                    "for_strat_canopy_e",     
                    "for_strat_aerial_e",     
                    "for_strat_spec_level",     
                    "for_strat_source_e",     
                    "body_mass_e",     
                    "body_mass_level_e",     
                    "body_mass_source_e",     
                    "body_size_mm",     
                    "body_size_notes",     
                    "body_size_level",     
                    "body_size_source",     
                    "sexual_dimorphism",     
                    "sexual_dimorphism_notes",     
                    "sexual_dimorphism_level",     
                    "sexual_dimorphism_source",     
                    "longevity",     
                    "longevity_notes",     
                    "longevity_level",     
                    "longevity_source",     
                    "home_range_size",     
                    "home_range_notes",     
                    "home_range_level",     
                    "home_range_source",     
                    "habitat_specialization",     
                    "habitat_specialization_source",     
                    "generation_time",     
                    "generation_time_notes",     
                    "generation_time_level",     
                    "generation_time_source",     
                    "IUCN_category",     
                    "habitat",     
                    "habitat_breadth",     
                    "habitat_breadth_source",     
                    "habitat_level",     
                    "mean_CHELSA_bio1_1981.2010_V.2.1",     
                    "mean_CHELSA_bio12_1981.2010_V.2.1",     
                    "mean_human_fp_range_2010",     
                    "mean_human_fp_range_2020",     
                    "percent_change_hf_2010_2020",     
                    "inferred_range_sqkm",     
                    "date_data_obtained",     
                    "filled_by"    ), check.names=TRUE)

unlink(infile4)

# Fix any interval or ratio columns mistakenly read in as nominal and nominal columns read as numeric or dates read as strings

if (class(Frug_bird$IUCN_species_name)!="factor") Frug_bird$IUCN_species_name<- as.factor(Frug_bird$IUCN_species_name)
if (class(Frug_bird$common_name)!="factor") Frug_bird$common_name<- as.factor(Frug_bird$common_name)
if (class(Frug_bird$family_e)!="factor") Frug_bird$family_e<- as.factor(Frug_bird$family_e)
if (class(Frug_bird$genus)!="factor") Frug_bird$genus<- as.factor(Frug_bird$genus)
if (class(Frug_bird$species)!="factor") Frug_bird$species<- as.factor(Frug_bird$species)
if (class(Frug_bird$elton_species_name)!="factor") Frug_bird$elton_species_name<- as.factor(Frug_bird$elton_species_name)
if (class(Frug_bird$diet_cat_e)!="factor") Frug_bird$diet_cat_e<- as.factor(Frug_bird$diet_cat_e)
if (class(Frug_bird$diet_source_e)!="factor") Frug_bird$diet_source_e<- as.factor(Frug_bird$diet_source_e)
if (class(Frug_bird$diet_breadth)=="factor") Frug_bird$diet_breadth <-as.numeric(levels(Frug_bird$diet_breadth))[as.integer(Frug_bird$diet_breadth) ]               
if (class(Frug_bird$diet_breadth)=="character") Frug_bird$diet_breadth <-as.numeric(Frug_bird$diet_breadth)
if (class(Frug_bird$diet_level)!="factor") Frug_bird$diet_level<- as.factor(Frug_bird$diet_level)
if (class(Frug_bird$activity_nocturnal_e)!="factor") Frug_bird$activity_nocturnal_e<- as.factor(Frug_bird$activity_nocturnal_e)
if (class(Frug_bird$for_strat_ground_e)=="factor") Frug_bird$for_strat_ground_e <-as.numeric(levels(Frug_bird$for_strat_ground_e))[as.integer(Frug_bird$for_strat_ground_e) ]               
if (class(Frug_bird$for_strat_ground_e)=="character") Frug_bird$for_strat_ground_e <-as.numeric(Frug_bird$for_strat_ground_e)
if (class(Frug_bird$for_strat_understory_e)=="factor") Frug_bird$for_strat_understory_e <-as.numeric(levels(Frug_bird$for_strat_understory_e))[as.integer(Frug_bird$for_strat_understory_e) ]               
if (class(Frug_bird$for_strat_understory_e)=="character") Frug_bird$for_strat_understory_e <-as.numeric(Frug_bird$for_strat_understory_e)
if (class(Frug_bird$for_strat_midhigh_e)=="factor") Frug_bird$for_strat_midhigh_e <-as.numeric(levels(Frug_bird$for_strat_midhigh_e))[as.integer(Frug_bird$for_strat_midhigh_e) ]               
